\LARGE Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-08 poster/main.tex
update poster

\begin{block}{Objectives}
\noindent Design a tool for differentially private probabilistic
programming featuring:
\begin{enumerate}
\item programming constructs to describe bayesian models and perform probabilistic inference,
\item programming constructs useful to ensure differential privacy,
\item type-checking as a method to ensure that the actual programs are
  differentially private.
\end{enumerate}

@@

\begin{block}{Some Experimental Results}
\begin{figure}[H]
\begin{center}
\centering
  \subfigure[Data set size from $300$ to $800$ ]{
    \includegraphics[width=0.39\textwidth]{poster_1.eps}
    \label{fig_1}
  }
  \subfigure[Data set size from $14000$ to $20000$]{
    \includegraphics[width=0.352\textwidth]{poster_2.eps}
  \label{subsubsec_vs_datasize1b}} 
\caption{Increasing data size with fixed prior $\betad(1,1)$. Unbalanced datasets of mean $(0.1,0.9)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
\label{fig_vs_datasize}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\centering
  \subfigure[Data set size from $300$ to $800$ ]{
    \includegraphics[width=0.372\textwidth]{poster_3.eps}
    \label{subsubsec_vs_datasize1a}
  }
  \subfigure[Data set size from $14000$ to $20000$]{
    \includegraphics[width=0.32\textwidth]{poster_4.eps}
  \label{subsubsec_vs_datasize1b}} 
\caption{Increasing data size with fixed prior $\betad(1,1)$. Unbalanced datasets of mean $(0.1,0.9)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
\label{fig_vs_datasize}
\end{center}
\end{figure}

>>>>

\begin{block}{Objectives}
\noindent Design a mechanism that achieve differential privacy by scaling to a metric between distribution.
\begin{enumerate}
\item A differentially private bayesian mechanism,
\item Calibrating mechanism noise by the same probabilistic distance we want to measure accuracy with.
\item Applying smooth sensitivity in mechanism to achieve better accuracy.
\end{enumerate}

@@

\begin{block}{Some Experimental Results}
\begin{figure}[H]
\begin{center}
\centering
  \subfigure[\footnotesize{2-dimensional, data size $\in [100,500]$}]{
    \includegraphics[width=0.328\textwidth]{poster_1.eps}
    \label{fig_1}
  }
  \subfigure[\footnotesize{3-dimensional, data size $\in [100,500]$} ]{
    \includegraphics[width=0.297\textwidth]{poster_2.eps}
  \label{subsubsec_vs_datasize1b}} 
  \subfigure[\footnotesize{4-dimensional, data size $\in [100,600]$}]{
    \includegraphics[width=0.29\textwidth]{poster_3.eps}
    \label{subsubsec_vs_datasize1a}
  }
  \caption{Increasing data size with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
\label{fig_vs_datasize}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\centering
  \subfigure[2-dimensional]{
    \includegraphics[width=0.31\textwidth]{poster_4.eps}
  \label{subsubsec_vs_datasize1b}}
  \subfigure[3-dimensional]{
    \includegraphics[width=0.31\textwidth]{poster_5.eps}
  \label{subsubsec_vs_datasize1b}} 
  \subfigure[4-dimensional]{
    \includegraphics[width=0.31\textwidth]{poster_6.eps}
  \label{subsubsec_vs_datasize1b}} 
\caption{The concrete outputting probabilities under different dimensions with data set of size $600$ ,unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
\label{fig_vs_datasize}
\end{center}
\end{figure}
